\chapter*{Dedication}
%===================================================================

I couldn't be the person I'am today and accomplish anything in my life including this project without the help of everyone who believed in me from day one and especially :\newline


My mother \textbf{Salwa}  who dedicated her life to my sisters and I's success, she sheltered us from any thing that could've altered our path.\newline

My father \textbf{Rafik}  who made our life feels so comfortable and easy throughout the years, bravely taking all life problems and pain without ever letting trouble reach our home.\newline  

My Aunt \textbf{Salma} for taking me under her wings from the day i moved to Tunis and counting me as a son among her children.\newline

My \textbf{Family} for being the greatest people to grow up among, teaching me the best life lessons and making the best possible environment to became the best person i could be.\newline

My \textbf{Friends} for being the inspiration during all of this years, for being the support and motivation that get me to the next step in my life. I couldn't be here without each and everyone of you, and i'll always be there for you.\newline

\begin{center}
	\textbf{To every one who is special to me, I dedicate this work}
\end{center}


\chapter*{Acknowledgments}

This work would not have been possible without the valuable cooperation of a number of people I want to pay tribute to.\newline

I would like to thank all those who have made this internship a rewarding and enjoyable experience, especially :\newline

\textbf{Mr Nebras JEMAL}, co-founder and CEO of Flouci for believing in me from day one, my internship tutor \textbf{Mr Anis KALLEL} co-founder and CTO who introduced me to the team and helped me throughout my journey. Thank you for your advice and help throughout the internship. \newline

The \textbf{"Flouci"} team, my second family, for their support, advice and all their devotion and passion to what we are doing.\newline

I would particularly like to thank my supervisor \textbf{Mr Aymen SELLOAUTI} for he availability, remarks and advice. I also would like to express my respect and my gratitude to him\dots\newline

Finally, I also express my sincere recognition to the members of the jury : \textbf{Mr Flen} and \textbf{Mr Flen} for accepting to evaluate my work.